---
title: "Our program"
description: |
 Master of Oceanography of the Institute of Oceanography
---

## Presentation

Our master program was created in <mark>19XX</mark> and has since formed over <mark>xxxx</mark> students. It is composed of four specialities: marine biology and fisheries, physical oceanography, chemical oceanography, marine geology and geophysics that will provide the students with expertise in one of those areas.


## Objectives

Our master program is designed to prepare students, in two years, for a career in marine  research, teaching, and other environmentally related endeavors. After graduation, some may continue and purchase a Ph.D. in a related field. To contrast, some may decide to look at professional opportunities.

## Statistics

From our record on the employment status of IONTU's graduated students  (Years 2014-19):


### Master Degree

A vast majority of our Master's graduates work for private companies or governmental/research institutes  

```{r, echo=F, fig.cap="Employment status Master IONTU's graduates (n=16, 2014-2019)"}
library(plotrix)
library(RColorBrewer)
slices <- c(37, 58, 61, 3,6, 15, 4)
lbls <- c("others", "governmental/research institutes", "private company", "work aboard", "school teacher", "study further","start a business")
a <- pie3D(slices, radius = 0.8, explode = 0.05, mar = c(0,0,0,0), col=brewer.pal(5,"RdGy"))
pie3D.labels(a, radius = 1.1, labels = lbls, labelcex = 0.7)
```

### PhD Degree

A vast majority of our Ph.D.'s graduates work for governmental/research institutes  

```{r, echo=F, fig.cap="Employment status Ph.D. IONTU's graduates (n=16, 2014-2019)"}
library(plotrix)
library(RColorBrewer)
slices <- c(1, 9, 1, 1,2, 2)
lbls <- c("others", "governmental/research institutes", "private company", "professor", "work aboard", "school teacher" )
a <- pie3D(slices, radius = 0.8, explode = 0.05, mar = c(0,0,0,0), col=brewer.pal(5,"RdGy"))
pie3D.labels(a, radius = 1.1, labels = lbls, labelcex = 0.7)
```

## Admission

The fundamental requirement for admission to the program is a strong motivation for ocean sciences and an aptitude for original research. The preparation for admission to our graduate program should comprise an undegraduate degree in the discipline  of one of the program specialties or an an equivalent background. If a student does not have a degree in one of these areas, the student must demonstrate that they have taken the classes necessary to do their research. It is strongly recommended that students applying prealably contact a sponsor professor to discuss the relevance of the study they want to develop. A list of the professor by speciality together with their contact is available on the website of the Institute of Oceanography (http://www.oc.ntu.edu.tw/oceng). It is possible to have a project co-advised with external researcher of the institute. In this case, it is also strongly recommended that the student discuss about the possibility to be co-advised. 

 
## Graduation

A minimum of 24 credits plus a master thesis are required to graduate. 